### 2009-05-12 doc/tech_doc/jura/jura-tech-doc.tex
added to/changed tech doc

\section{Implementation}
\label{implement}
JURA is written merely in C++, built with standard GNU tools, and
tested in a GNU/Linux environment. It depends on HED libraries: the
common utilities library, the message handling library and the Message
Chain Components for the TCP, TLS, SOAP and HTTP protocols. It also
depends on all mandatory dependencies of ARC: gthread-2.0, glibmm-2.4,
libxml-2.0, openssl, e2fsprogs and GNU gettext.

@@

%TODO implement!
where \textit{size} is a positive integer, the number of URs sent
within one request. If not given, the default is 50. Zero value means
unlimited batch size.

%EXAMPLE!

@@

\section{Limitations and future plans}
\label{future}
Although complete, JURA still has minor imperfections, some of them
stemming from flaws in A-REX or the \textit{arcsub} client:

\begin{itemize}
\item The time frequency of running JURA is not configurable. It is a
  hardcoded value in A-REX: 3600 seconds, i.e. one hour. 
\item The number of user-supplied reporting destinations is limited
  for the sake of robustness. This upper limit is hardcoded in A-REX:
  max. 3 destinations are parsed from JSDL, and max. 1 from RSL.
\item The \textit{arcsub} job submission client removes all but one
  reporting destination URL from the job description, further limiting
  the number of user-supplied destinations.
\item The current implementation of JURA and A-REX supports only one
  expiration time for all the reporting destinations. Even though the
  configuration enables the specification of different expiration
  values per reporting destination, it is not taken into account by
  the system, the last value is used as the common expiration time
  value.
\item It is not possible to use different credentials per destinations.
\item Some optional UR properties are not supported (see
  App.~\ref{log2ur}).
\item Memory is not reported correctly. A bug in GNU ``time'' results
  in all memory usage set incorrectly as zero.
\item Some necessary extensions to the generated UR are not yet filled
  though the information is already collected in the job log files.
\item Handling of runtime environment string is missing.
\item Detailed user identity information based on proxy or other
  submitted credentials is missing from URs.
\end{itemize}

>>>>

\section{Implementation}
\label{implement}
JURA is written merely in C++, built with widely used GNU tools, and
tested in a GNU/Linux environment. It depends on HED libraries: the
common utilities library, the message handling library and the Message
Chain Components for the TCP, TLS, SOAP and HTTP protocols. It also
depends on all mandatory dependencies of ARC: gthread-2.0, glibmm-2.4,
libxml-2.0, openssl, e2fsprogs and GNU gettext.

@@

where \textit{size} is a positive integer, the number of URs sent
within one request. If not given, the default is 50. Zero value means
unlimited batch size.

The example below is a part of the ``\textit{grid-manager}'' block of
the A-REX configuration. It enables logging of URs to two hosts, using
the host credential files (placed in the standard locations), with a
maximum of 50 URs per batch. Job log files expire after a week.
%EXAMPLE!
\begin{verbatim}
...
jobreport="https://luts1.nordugrid.org:8443/wsrf/services/sgas/LUTS"
jobreport="https://luts2.nordugrid.org:8443/wsrf/services/sgas/LUTS 7"
jobreport_credentials="/etc/grid-security/hostkey.pem /etc/grid-security/hostcert.pem 
     /etc/grid-security/certificates"
jobreport_options="urbatch:50"
...
\end{verbatim}

@@

\section{Limitations and future plans}
\label{future}
Although complete, JURA still has minor imperfections, some of them
stemming from limitations or operational characteristics of A-REX or
the \textit{arcsub} client:

\begin{itemize}
\item The time frequency of running JURA is not configurable. It is a
  hardcoded value in A-REX: 3600 seconds, i.e. one hour. 
\item The number of user-supplied reporting destinations is limited
  for the sake of robustness. This upper limit is hardcoded in A-REX:
  max. 3 destinations are parsed from JSDL, and max. 1 from RSL.
\item The \textit{arcsub} job submission client removes all but one
  reporting destination URL from the job description, further limiting
  the number of user-supplied destinations.
\item The current implementation of JURA and A-REX supports only one
  expiration time for all the reporting destinations. Even though the
  configuration enables the specification of different expiration
  values per reporting destination, it is not taken into account by
  the system, the last value is used as the common expiration time
  value.
\item It is not possible to use different credentials per destinations.
\item Some optional UR properties are not supported (see
  App.~\ref{log2ur}).
\item Memory is not reported correctly. A bug in GNU ``time'' results
  in all memory usage set incorrectly as zero.
\item Some necessary extensions to the generated UR are not yet filled
  though the information is already collected in the job log files.
\item Handling of runtime environment string is missing.
\item Detailed user identity information based on the X.509 proxy
  certificate content or other submitted credentials is missing from
  URs.
\end{itemize}
